### 2021-10-11 docs/paper/sections/3_approach/usage_mining/patterns/JsxOpeningElement.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting
Improve black/white accessibility of figure 2

\begin{tikzpicture}
	\node [accent1] {JsxOpeningExpression}
		child [gray] {node [gray] {tagName}}
		child [gray] {node [gray, yshift = -0.5cm] {typeArguments}}
		child [gray] {node [gray] {attributes}};
\end{tikzpicture}
\caption[LoF entry]{
	Node pattern for a JSX opening element (as supported in React\footnote{\url{https://reactjs.org/docs/introducing-jsx.html}} or TypeScript\footnote{\url{https://www.typescriptlang.org/docs/handbook/jsx.html}}), such as in:
	\code{\textlowlight{elem = }\uline{<Button \textlowlight{color}="\textlowlight{blue}"> \textlowlight{Submit</Button>}}\textlowlight{;}}
}

>>>>

\begin{tikzpicture}
	\node [accent1] {\textbf{JsxOpeningExpression}}
		child [lowlight] {node [lowlight] {tagName}}
		child [lowlight] {node [lowlight, yshift = -0.5cm] {typeArguments}}
		child [lowlight] {node [lowlight] {attributes}};
\end{tikzpicture}
\caption[LoF entry]{
	Node pattern for a JSX opening element (as supported in React\footnote{\url{https://reactjs.org/docs/introducing-jsx.html}} or TypeScript\footnote{\url{https://www.typescriptlang.org/docs/handbook/jsx.html}}), such as in:
	\code*{\textlowlight{elem = }\uline{<\texthighlight{Button} \textlowlight{color}="\textlowlight{blue}"> \textlowlight{Submit</Button>}}\textlowlight{;}}
}
